\section{communication}
When it comes to communication, outside of the already existing platforms that were set up beforehand for having good engagement (Mattermost and Gitlab), we have made sure we had other channels through which we could reach out to the team members.\par
\smallskip
First, we created a WhatsApp group that allows us to easily send messages and speak out our concerns and on top of that request feedback for our merge requests and new commits that we have implemented. Secondly, we have built up a Discord server that would allow us to have meetings remotely and conversations in the voice channels. Also, we can put the most important resources, documents and ongoing issues in the "important-links" and "tasks" text channels. In addition, it is a great platform in which we can enter at any time from anywhere with a teammate when we are facing an issue, so it makes collaborating much more feasible. \par
\smallskip
After the creation of these channels, we agreed upon a mandatory meeting every Monday at 7 p.m. on our Discord server in which we would check on both our individual and team progress. This way, we can always stay up to date with each other, discuss the issues we are currently facing with the development of our application and assign tasks more clearly than we have already done in the official meeting. \par
\smallskip
One more important aspect of communication is not only staying in touch with our teammates but our assigned TA as well and we are doing that through Mattermost, where we ask questions about tasks that we feel are unclear or make sure we are having a correct approach when it comes to the project. Moreover, we try to be as punctual as possible when it comes to sharing the week's agenda and minutes on GitLab and additionally have a team member write a report that will be shared on Mattermost for a better collaboration with our TA.\par



