\section{Shared Team Values}
First and foremost, the most significant team values that we represent are mutual respect and inclusion. No matter the discrepancies between knowledge, skill and intellect, we must always seek to find the best value every member brings to the group and everyone's voice is heard. This helps every member grow, feel included when developing these tasks and makes the working environment feel like a safe space and prone to evolution.\par
\smallskip
The next values are innovation and creativity. What we are looking to achieve by the end of this project is not only a basic application but rather exploring and finding new ideas and technology and finding unique ways to solve problems. Not only does it allow us to build up critical thinking, but also understand what we are working on and makes the addition of changes much more feasible.\par
\smallskip
Two more important factors are agility and flexibility. Since the workload is complicated to comprehend at first and the information is new for everyone, we have to be able to adapt on the go. This takes a lot of focus, rapid learning and also deep understanding of what we are trying to create. Each week represents a new challenge, having to come up with fresh ideas for every feature we are striving to implement.\par
\smallskip
Last but not least we have integrity and transparency. It is of utmost importance to maintain honesty between us and gain trust in each other. Trust is fundamental when we are in an environment that pressures everyone since we need to be together in both our worst and best moments. Thus, we can create a workspace that allows us to transcend the ideology of a university project and feel like we are in an actual company, developing our next new feat.\par



